Variational Monte Carlo on Bosonic Systems

### 2018-04-05 project_1/article/article.tex
Add TODO
Rewrote introduction.

    First, we start by explaining our theoretical quantum system of a bosonic
    gas trapped in a potential well. Here we also outline the principle under
    which particles in the gas are allowed to interact. Moreover, we introduce
    the \emph{local energy} and the quantum \emph{drift force}. Here we also
    outline in more detailed algebra the nature of a non-interacting system. For
    this system we are able to derive an exact variational energy to which we
    can compare the results from our simulations. We furthermore give a
    description of the particle-particle interaction implemented as if each
    particle is a hard sphere. Second, we provide a thorough description of
    algorithms and statistical methods employed in this study. Here we introduce
    the Metropolis-Hastings algorithm. This algorithm can by a deft trick be
    expanded with the method of \emph{importance sampling} yielding a more
    intelligent choice for the next step in the Monte Carlo steps.

    The main point of note with regards to the statistical analysis is that the
    data generated by the Monte Carlo cycling is autocorrelated and computation
    of variance must be done with the \emph{blocking method}.  As an automated
    way of finding the optimal variational parameter, we sketch out the method
    of \emph{gradient descent}.  Third, we put the machinery described in the
    previous sections to work. We test against the actual values in a
    non-interacting system before analysing the more interesting perturbed-trap
    system with interacting particles.  Lastly, we highlight the more
    interesting aspects of this study in a discussion of the results before
    ending on some summary remarks.

@@

>>>>

	First, we provide the theoretical foundation for the Variational Monte Carlo
	method. This includes explaining how Monte Carlo integration works, and
	introducing the important quantities \emph{local energy}, \emph{drift force}
	and \emph{one-body densities}.

    Second, we outline in more detailed algebra the nature of a systems we will
    be studying. For
    the non-interacting system we are able to derive an exact variational energy 
    to which we
    can compare the results from our simulations. We furthermore give a
    description of an interacting system implemented as if each
    particle is a hard sphere.

    Third, we provide a thorough description of
    algorithms and statistical methods employed in this study. Here we introduce
    the Metropolis-Hastings algorithm. This algorithm can by a deft trick be
    expanded with the method of \emph{importance sampling} yielding a more
    intelligent choice for the next step in the Monte Carlo cycling.
    The main point of note with regards to the statistical analysis is that the
    data generated by the Monte Carlo cycling is autocorrelated and computation
    of variance must be done with the \emph{blocking method} for time series data. 
    As an automated
    way of finding the optimal variational parameter, we sketch out the method
    of \emph{gradient descent}.

    Fourth, we put the machinery described in the
    previous sections to work. We test against the actual values in a
    non-interacting system before analysing the more interesting perturbed-trap
    system with interacting particles.

    Lastly, we highlight
    interesting aspects of this study in a discussion of the results before
    ending on some summary remarks.

@@

    \subsection{One-Body Densities}
        % TODO: Fill in this
